Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-08-19 content.tex
Use newer figures
Minor rephrasing in twin alignment construction

From the twin tree, we simulate an alignment following the same
history as the twin tree, using the same mutation rate,
with the constraint that 
the same total number of mutations have
taken place.
This constraint ensures there is the same amount of historical information
stored in both the true and twin alignments.
We achieve this by simply simulating twin alignments until we
obtain one that has the desired number of mutations.

@@

We start from the tree generated by a non-standard (and unknown) tree prior, 
having six taxa and a crown age of ten:
\begin{lstlisting}[
  language = R, 
  floatplacement = ht,
  frame = single, 
  label = {lst:unknown_phylogeny},
  caption = A phylogeny generated by an unknown diversification model.
]
phylogeny  <- ape::read.tree(
  text = "(((A:8, B:8):1, C:9):1, ((D:8, E:8):1, F:9):1);"
)
\end{lstlisting}
\begin{figure}[H]
  \includegraphics[width=\textwidth]{example_6/true_tree.png}
  \caption{The tree derived from an unknown diversification process, 
    as created by listing~\ref{lst:unknown_phylogeny}.
    The scale overlaps with the lower branch, which is the default 
    behavior for the plotting function used.
  }
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{example_6/errors.png}
  \caption{
    The inference error made 
    for both a generative tree prior and best candidate model
    compared with the error obtained for the twin tree.
    Here, the 'twin' tree shows the baseline inference error.
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_3}
\end{figure}

>>>>

From the twin tree, we simulate an alignment following the same
history as the twin tree, using the same mutation rate,
with the constraint that 
the exact same total number of mutations have
taken place from the phylogeny's root sequence and all sequences at the tips. 
We achieve this by simply simulating twin alignments until we
obtain one that has the desired number of mutations.
This constraint ensures there is approximately 
the same amount of historical information
stored in both the true and twin alignments.

@@

We start from the tree generated by a non-standard (and unknown) tree prior, 
having six taxa and a crown age of ten:
\begin{lstlisting}[
  language = R, 
  floatplacement = ht,
  frame = single, 
  label = {lst:unknown_phylogeny},
  caption = A phylogeny generated by an unknown diversification model.
]
phylogeny  <- ape::read.tree(
  text = "(((A:8, B:8):1, C:9):1, ((D:8, E:8):1, F:9):1);"
)
\end{lstlisting}
\begin{figure}[H]
  \includegraphics[width=\textwidth]{example_3/true_tree.png}
  \caption{The tree derived from an unknown diversification process, 
    as created by listing~\ref{lst:unknown_phylogeny}.
    The scale overlaps with the lower branch, which is the default 
    behavior for the plotting function used.
  }
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{example_3/errors.png}
  \caption{
    The inference error made 
    for both a generative tree prior and best candidate model
    compared with the error obtained for the twin tree.
    Here, the 'twin' tree shows the baseline inference error.
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_3}
\end{figure}
